Parsing Tweets into Universal Dependencies

### 2018-03-04 paper.tex
authors

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{naaclhlt2018}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{tikz-dependency}
\usepackage{url}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{arydshln}
\newcommand\BibTeX{B{\sc ib}\TeX}
\DeclareMathOperator*{\argmin}{argmin}
\def\aclpaperid{214}
%%%%%%%
\usepackage{graphicx}
\newcommand{\heart}{\ensuremath\heartsuit}

@@

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{naaclhlt2018}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{tikz-dependency}
\usepackage{url}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{arydshln}
\newcommand\BibTeX{B{\sc ib}\TeX}
\DeclareMathOperator*{\argmin}{argmin}
%\def\aclpaperid{214}
\aclfinalcopy
%%%%%%%
\usepackage{graphicx}
\newcommand{\heart}{\ensuremath\heartsuit}

@@

\author{Yijia Liu \\
  Harbin Institute of Technology \\
  {\tt oneplus.lau@gmail.com} \\\And
  Yi Zhu \\
  University of Cambridge \\
  {\tt yz568@cam.ac.uk} \\\AND
  Wanxiang Che \quad Bing Qin\\
  Harbin Institute of Technology\\\And
  Nathan Schneider \\
  Georgetown University \\\And
  Noah A. Smith \\
  University of Washington
  }
